Real-time Attention Assessment for Social Robots

### 2015-09-14 paper.tex
Commented out for now out-of-scope parts of intro

\section{Introduction: Attention and Engagement}
In the recent years, research is pushing forward in building intelligent systems
and environments that try to maximize the benefits of cooperation with humans
based on verbal and non-verbal communication. The interaction between social
robots and humans entails a broad set of situations, and evidences the need for
capturing significant backchannel information generated by the user during the
interaction process. Such information is used to adapt the system to the
specific user's needs to eventually provide a social or emotional intelligence
to the agents.

It is indeed not enough to exhibit human-like capabilities in social tasks: a
robot needs to achieve human-like manners. For instance, several studies showed
that humans prefer to interact with robots whose task outcome is delayed, shows
uncertainty or an undesired output \cite{Admoni,Short}. In fact, the ability to
adapt has been proved to be beneficial in long-term interactions
\cite{Tielman:2014, Lim:2014}, specifically with children, manifesting a more
positive attitude over time.

>>>>

\section{Introduction: Attention and Engagement}
%In the recent years, research is pushing forward in building intelligent systems
%and environments that try to maximize the benefits of cooperation with humans
%based on verbal and non-verbal communication. The interaction between social
%robots and humans entails a broad set of situations, and evidences the need for
%capturing significant backchannel information generated by the user during the
%interaction process. Such information is used to adapt the system to the
%specific user's needs to eventually provide a social or emotional intelligence
%to the agents.
%
%It is indeed not enough to exhibit human-like capabilities in social tasks: a
%robot needs to achieve human-like manners. For instance, several studies showed
%that humans prefer to interact with robots whose task outcome is delayed, shows
%uncertainty or an undesired output \cite{Admoni,Short}. In fact, the ability to
%adapt has been proved to be beneficial in long-term interactions
%\cite{Tielman:2014, Lim:2014}, specifically with children, manifesting a more
%positive attitude over time.
